---
title: "Lab 05 - Multiple Linear Regression"
date: "2022-10-27"
format: 
  html:
    self-contained: true
    theme:
      - flatly
      - lab.scss
---

**Due:** 2022-11-02 at 11:59pm
**Turn your .html file in on Canvas**

# Getting started

Go to RStudio Pro and click:

**Step 1**. File \> New Project\
**Step 2**. "Version Control"\
**Step 3**. Git\
**Step 4**. Copy the following into the "Repository URL":

```{bash}
#| eval: false
https://github.com/sta-112-f22/lab-05-multiple-linear-regression.git
```

# Exercises

```{r}
#| include: false
library(tidyverse)
library(Stat2Data)
```

The `Diamonds` data set can be used to examine the predict a diamond's price using characteristics about the diamond. For this lab, you need to try to find the **best model** to predict the total price of a diamond. Here "best" is defined as a model that (1) meets the assumptions of multiple regression and (2) has a good model fit, as determined by the metrics we've learned so far. I want you to **show your work**. Your report should include:

(1) A list of all models you attempted
(2) Figures displaying the checks for the assumptions for multiple linear regression for the **final model you pick**
(3) The equation for the **final model you pick**
(4) The model goodness of fit metric for the **final model you picked** (and how it compared to the other models)
(5) Finally, I want you to use this new data set below to predict what a **particular** diamond with these specifications would cost, along with an appropriate confidence interval. (Note: it is not a problem if you do not include all of these variables in your model)

```{r}
new_data <- data.frame(
  Carat = 2,
  Color = "J",
  Clarity = "SI2",
  Depth = 69
)
```



Some things to consider: you may want to try transformations of the outcome, include polynomial terms to account for non-linearity, and/or include interaction terms. Also, be sure to carefully understand what each of the available variables mean. It would not make sense to use a function of the outcome in the model, for example.
